\documentclass{article}

\usepackage[left=1.4in,right=1.4in,top=1.3in,bottom=1.3in]{geometry}

\usepackage[parfill]{parskip}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}

\cfoot{\thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
  {\Large Erroll Wood}
  
  \small{
	  +44 7738 717662 $\cdot$ erroll.wood@cl.cam.ac.uk $\cdot$ www.errollw.com \\
	  Gonville \& Caius College $\cdot$ Cambridge $\cdot$ CB2 1TA \\
  }
\end{center} \medskip 

\textsc{Education} \smallskip \hrule \smallskip
\textbf{Cambridge University, Gonville \& Caius College} \hfill 2009 -- \emph{present} \\[-4mm]

\begin{itemize}
  \item[]
  PhD in progress on pervasive eye tracking for large displays (supervisor: Peter Robinson). \
  %hfill (\emph{present})
  
  \textbf{MEng, Distinction} -- \emph{Computer Science Tripos Part III} \hfill 2013 \\
  Dissertation: \textsc{Gaze Estimation for Portable Devices}. Developed a
  gaze-tracking system suited for commodity portable devices, taking the limited image sensors and typical use environments into account (supervisor: Andreas Bulling).

  \textbf{BA, Class I} -- \emph{Computer Science Tripos Part II} \hfill 2012 \\
  Dissertation: \textsc{3D Fractal Exploration using a Scale-Adaptive Sparse Voxel Octree}. Developed a system for procedurally generating and rendering 3D fractals in real time, independent of the scale they are explored at (supervisor: Alex Benton).
\end{itemize} \smallskip

\textbf{St Paul's School, London} \hfill 2004 -- 2009 \\[-6mm]
\begin{itemize}
  \item[]
  A-Levels: A in Maths, Further Maths, Physics and Computing [A2], A in Economics [AS] \\
  GCSEs: 10 A\raise0.2ex\hbox{*}s and 1 A grade
\end{itemize} \bigskip

\textsc{Internships} \smallskip \hrule \smallskip

\textbf{Microsoft Research Cambridge} -- \emph{Intern} \hspace*{\fill} Winter
2015 \\[-6mm]
\begin{itemize}
  \item[]
  Used a hand-tracker to explore the effects of different types of virtual hand embodiments on remote collaboration for large displays (host: Jamie Shotton).
\end{itemize} \smallskip

\textbf{Cambridge University Computer Lab} -- \emph{Research intern} \hspace*{\fill} Summer
2013 \\[-6mm]
\begin{itemize}
  \item[]
  Developed an interactive networked public noticeboard framework to facilitate remote communication and group awareness (NetBoards).% Computer lab members can edit the noticeboards in person, or via web-apps on desktop or mobile.
\end{itemize} \smallskip

\textbf{Qualcomm Research, Cambridge} -- \emph{Software engineer intern} \hspace*{\fill} Summer
2012 \\[-6mm]
\begin{itemize}
  \item[] Developed Android clients to showcase and test context-aware services.
  %Presented a demo to Irwin and Paul Jacobs (Qualcomm's Chair and CEO).
  Researched privacy concerns for Android, focussing on context-aware data collection.
  % Examined both technical (taint-analysis) and user-experience aspects.
\end{itemize} \smallskip

\textbf{Credit Suisse} -- \emph{Lead software engineer intern} \hfill Summer 2011 \\[-6mm]
\begin{itemize}
  \item[] Lead developer in a team of 13 interns. Developed a real-time server monitoring web-app which was deployed by the company.
  % Delivered a presentation and demo to $\sim\!40$ interns and staff.
\end{itemize} \smallskip

\textbf{Succeed Consultancy} -- \emph{Software engineer intern} \hfill Summer 2010 \\[-6mm]
\begin{itemize}
  \item[] Produced plug-ins and unit tests for load-testing employee management software.
\end{itemize} \smallskip

\textbf{Symbian Foundation} -- \emph{Work experience} \hfill Summer 2009 \\[-6mm]
\begin{itemize}
  \item[] Documented the process of porting Flash apps to Flash Lite for mobile.
\end{itemize} \smallskip

\textbf{Microsoft Research Cambridge} -- \emph{Work experience} \hfill Winter 2008 \\[-6mm]
\begin{itemize}
  \item[] Developed a Flash web applet for the Environmental Science Dept. to help present their study on birds' flight patterns.
\end{itemize} \bigskip

\textsc{Publications} \smallskip \hrule \smallskip

\textbf{Learning an Appearance-Based Gaze Estimator from One Million Synthesized Images} \hfill 2016 \\[-6mm]
\begin{itemize}
  \item[] Erroll Wood, Tadas Baltrusaitis, Louis-Philippe Morency, Peter Robinson, Andreas Bulling \\
  \emph{Eye Tracking Research \& Applications, 2016 (to appear)}
\end{itemize} \smallskip

\textbf{Rendering of Eyes for Eye-Shape Registration and Gaze Estimation} \hfill 2015 \\[-6mm]
\begin{itemize}
  \item[] E. Wood, T. Baltrusaitis, X. Zhang, Y. Sugano, P. Robinson, and A. Bulling \\
  \emph{International Conference on Computer Vision, 2015, poster}
\end{itemize} \smallskip

\textbf{NetBoards: Investigating a Collection of Personal Noticeboard Displays in the Workplace} \hfill 2014 \\[-6mm]
\begin{itemize}
  \item[] Erroll Wood and Peter Robinson \\
  \emph{Interactive Tabletops \& Surfaces, 2014, (invited demo)}
\end{itemize} \smallskip

\textbf{EyeTab: Model-based gaze estimation on unmodified tablet computers} \hfill  2014 \\[-6mm]
\begin{itemize}
  \item[] Erroll Wood and Andreas Bulling \\
  \emph{Eye Tracking Research \& Applications, 2014}
\end{itemize} \bigskip

\textsc{Awards \& Achievements} \smallskip \hrule \smallskip

\textbf{EPSRC Doctoral Training Studentship} \hfill 2013 \\[+1mm]
\textbf{Gonville \& Caius College Scholar} \hfill 2012 \\[+1mm]
\textbf{2\textsuperscript{nd} Year Group Project Prize} \hfill 2012 \\[+1mm]
\textbf{British Informatics Olympiad}, \emph{National Finalist} \hfill 2009 \\[+1mm]
\textbf{St Paul's School Senior Scholar} \hfill 2008 \\[+1mm]
\textbf{Duke of Edinburgh's Award}, \emph{Gold Level} \hfill 2008 \\[+1mm]
\textbf{Arkwright Engineering Scholar} under \emph{Microsoft Research Cambridge} \hfill 2007 \\

\textsc{Other Activities} \smallskip \hrule \smallskip

\textbf{University Teaching} \hfill 2013 -- \emph{present} \\[-6mm]
\begin{itemize}
  \item[]
  Taught Computer Vision, Graphics, Artificial Intelligence, and Information Theory to undergraduates for over 100 hours, supervised six final year projects, managed interns, and performed admissions interviews.
\end{itemize} \smallskip

\textbf{Gonville \& Caius May Ball Committee} -- \emph{Web \& Systems} \hfill 2011 -- 2014
\\[-6mm]
\begin{itemize}
  \item[]
  % Worked in a team of 23 to re-envision John Milton's \emph{Paradise Lost} as a high-budget formal ball, specializing in adapting the poem into the event's atmosphere and decor.
  Developed websites for two May Balls, handling ticketing, staffing, and exploring the themes. Implemented a networked mobile ticket scanning system for speeding up entry.
\end{itemize} \smallskip

\textbf{Game Development} -- \emph{Indie Game Developer} \hfill 2005 -- 2010 \\[-6mm]
\begin{itemize}
  \item[]
  Developed many web-based minigames using Flash. These were distributed over the
  internet, generating revenue via sponsorship and advertising.
  % \emph{Weapons of Maths Destruction 2} is a recent example which combined tank combat with maths
  % education to encourage learning.
\end{itemize} \bigskip

% \textsc{Technical Skills} \smallskip \hrule \medskip

% \begin{tabular}{@{}l@{$\quad$}l@{}}
%   \textbf{Programming}      & Python (OpenCV, NumPy, IPython), Java (Android), C++ \smallskip \\ 
%   \textbf{Tools}            & PyCharm, Eclipse (Android), Visual Studio, Github \smallskip \\ 
%   \textbf{Websites}         & Javascript (jQuery, Paper.js), HTML5, SASS (Bourbon, Neat) \smallskip \\
%   \textbf{Media}            & Photoshop, Illustrator, Office, \LaTeX \smallskip \\
% \end{tabular} \\ \medskip

\centering \small (last updated \today)

\end{document}
